Clean - An Abstract Imperative Programming Language and its Theory

### 2019-10-30 C11-BackEnds/Clean/document/root.tex
clean

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
\newcommand{\isactrlC}{{\bf C}}

@@

Clean's design strives for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately restrict
themselves to the most elementary infrastructure for these tasks. The package is intended to serve
as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, or for the test-generation
techniques described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}

>>>>

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'

@@

Clean's design strives for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately restrict
themselves to the most elementary infrastructure for these tasks. The package is intended to serve
as demonstrator semantic backend for Isabelle/C~\cite{Tuong-IsabelleC:2019}, or for the
test-generation techniques described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}
